### 2015-07-14 ids-fusion.tex
Indicated that the funnel is for one day.
Mods relevant to todo Review 3: Flavors of IDS

Existing \idses are not designed to work together as part of a
suite of sensors.  Instead, each program generates a separate,
often voluminous, stream of reports; fusing them into a coherent 
overview is left
% TODO restore to QR15
%as an exercise for
 to
the user. 
Ideally, network administrators would have a suite of different \idses active,
since different \ids approaches
% TODO restore to QR15
% --- network (NIDS) vs.\
% host-based (HIDS), signature vs.\ anomaly-based --- 
bring different
strengths and weaknesses.
%%
%% Hm, can we just get rid of the details NIDS/HIDS and
%% signature/anomaly comparisons, and keep just the takeaway? I don't
%% believe we refer to them after this. 
%%
Briefly, more accurate \idses have significantly higher software
administration burdens, and there is an inevitable tradeoff between
false positives and false negatives.
%%
%%Some systems aim to overcome the limitations of existing \idses by assembling 
%%a suite of
%%sensors.  This can be a very efficient way to overcome the problem
%%of false positives, but relies crucially on finding sensors that fail
%%relatively independently.  
%%
%% 
%% NIDS systems are easy to deploy; from only one
%% or two locations, they can watch all relevant traffic.  Unfortunately, they also have
%% substantial problems with false positives and false negatives, because they
%% don't ``know'' the meaning of the traffic they see.  Often they must draw
%% conclusions based only on information in packet headers (although some
%% systems do attempt to reconstruct higher level protocols from packet data),
%% and more extensive reasoning about traffic either would slow down the
%% network, or must ignore some packets altogether.
%% A HIDS may take into account much more information about the state
%% of a defended system, but installing HIDS pervasively involves deploying and
%% configuring much more software.  Typically HIDS are installed on only the most
%% critical assets.
%% 
%% Signature-based systems attempt to match patterns of known bad behavior.  Such
%% \idses are plagued by false negatives, both because of novel attacks for which
%% there are no patterns to match, and because of known %knowledgeable attackers take
%% countermeasures against signature identification (e.g.\ encrypting malware, or
%% permuting its structure).  Anomaly detectors are prone to false
%% positives: anomalies are often benignly anomalous,
%% not maliciously so.  Detectors often believe there is an
%% anomaly when none exists because computer usage patterns are
%% notoriously difficult to learn: they are often non-stationary, they vary
%% substantially from location-to-location, etc.
%% \draft{Add citations of papers on the challenges of anomaly detection.}

@@

Users regularly ignore or disable their {\idses}, unable to absorb
massive streams of false alarms.
%% TODO Restore for QR'15
%``Users attending an 'ABCs of IDS' event at London's City University yesterday
%  said more the 80 per cent of the alerts they received were false, with one
%  citing 60 alerts he had received about non-existent problems that morning at
%  0300''
% ~\cite{Register}.
Recently, Target is reported to have ignored warnings about the
data breach that resulted in theft of millions of credit
card records~\cite{TargetIgnoredIDS}:
``They are bombarded with alerts. They get so many that they just don't respond
to everything''~\cite{finkle14:_target}.
Figure
\ref{fig:workloadReduction} gives a sense of the gravity of this
problem. It shows how our earlier system was able to winnow
the 
flow of reports in a small corporate network~\anoncite{goldman:09Scyllarus}.
% Data reduction must join building a comprehensive overview
% and overcoming false positives and negatives as goals of \ids fusion.
\begin{figure}[t]
    \ifthenelse{\boolean{blackAndWhite}}{%
      \includegraphics[width=.45\textwidth]{figures/funnel-dup-cropped.pdf} }{%
    \includegraphics[width=.45\textwidth]{figures/funnel-dup-cropped.pdf}} 
  \centering
  \caption{Scyllarus workload reduction%
% Squash citation here; cited in sentence referencing figure.
%~\anoncite{goldman:09Scyllarus}
.}
  \label{fig:workloadReduction}
\end{figure}

>>>>

Existing \idses are not designed to work together as part of a
suite of sensors.  Instead, each program generates a separate,
often voluminous, stream of reports; fusing them into a coherent 
overview is left
% TODO restore to QR15
%as an exercise for
 to
the user. 
Ideally, network administrators would have a suite of different \idses active,
since different \ids approaches
% TODO restore to QR15
% --- network (NIDS) vs.\
% host-based (HIDS), signature vs.\ anomaly-based --- 
bring different
strengths and weaknesses, and have different ``fields of view.'' For example, local
privilege escalation attacks may be invisible to a NIDS; HIDS systems are more
accurate for many purposes, but impose higher administrative burdens because
they must be scattered around the defended network, rather that centrally
deployed like NIDS.  Signature-based IDSes provide fewer false positives, but
are more likely to be blind to zero-day attacks than anomaly-based systems.
%%
%% Hm, can we just get rid of the details NIDS/HIDS and
%% signature/anomaly comparisons, and keep just the takeaway? I don't
%% believe we refer to them after this. 
%%
% Briefly, more accurate \idses have significantly higher software
% administration burdens, and there is an inevitable tradeoff between
% false positives and false negatives.
% This tradeoff applies for all of the different varieties of IDS,
% for example NIDS or HIDS, signature-based, anomaly-detecting, various
% hybrids.

% clarification relevant to [[file:todo.txt::*Review%203:%20Flavors%20of%20IDS][Review 3: Flavors of IDS]]
We will not discuss the varieties of \idses further here -- there is a
voluminous literature on them.   The \emph{precise} nature of \ids weaknesses and
strengths is not critical to our investigation here, but the fact that there
\emph{are} such strengths and weaknesses is what motivates our information
fusion, and difficulties in modeling the events and sensors is what motivates
our use of qualitative methods.
%%
%%Some systems aim to overcome the limitations of existing \idses by assembling 
%%a suite of
%%sensors.  This can be a very efficient way to overcome the problem
%%of false positives, but relies crucially on finding sensors that fail
%%relatively independently.  
%%
%% 
%% NIDS systems are easy to deploy; from only one
%% or two locations, they can watch all relevant traffic.  Unfortunately, they also have
%% substantial problems with false positives and false negatives, because they
%% don't ``know'' the meaning of the traffic they see.  Often they must draw
%% conclusions based only on information in packet headers (although some
%% systems do attempt to reconstruct higher level protocols from packet data),
%% and more extensive reasoning about traffic either would slow down the
%% network, or must ignore some packets altogether.
%% A HIDS may take into account much more information about the state
%% of a defended system, but installing HIDS pervasively involves deploying and
%% configuring much more software.  Typically HIDS are installed on only the most
%% critical assets.
%% 
%% Signature-based systems attempt to match patterns of known bad behavior.  Such
%% \idses are plagued by false negatives, both because of novel attacks for which
%% there are no patterns to match, and because of known %knowledgeable attackers take
%% countermeasures against signature identification (e.g.\ encrypting malware, or
%% permuting its structure).  Anomaly detectors are prone to false
%% positives: anomalies are often benignly anomalous,
%% not maliciously so.  Detectors often believe there is an
%% anomaly when none exists because computer usage patterns are
%% notoriously difficult to learn: they are often non-stationary, they vary
%% substantially from location-to-location, etc.
%% \draft{Add citations of papers on the challenges of anomaly detection.}

@@

Users regularly ignore or disable their {\idses}, unable to absorb
massive streams of false alarms.
%% TODO Restore for QR'15
%``Users attending an 'ABCs of IDS' event at London's City University yesterday
%  said more the 80 per cent of the alerts they received were false, with one
%  citing 60 alerts he had received about non-existent problems that morning at
%  0300''
% ~\cite{Register}.
Recently, Target is reported to have ignored warnings about the
data breach that resulted in theft of millions of credit
card records~\cite{TargetIgnoredIDS}:
``They are bombarded with alerts. They get so many that they just don't respond
to everything''~\cite{finkle14:_target}.
Figure
\ref{fig:workloadReduction} gives a sense of the gravity of this
problem. It shows how our earlier system was able to winnow
the 
flow of reports in a small corporate network over a day of operation~\anoncite{goldman:09Scyllarus}.
% Data reduction must join building a comprehensive overview
% and overcoming false positives and negatives as goals of \ids fusion.
\begin{figure}[t]
    \ifthenelse{\boolean{blackAndWhite}}{%
      \includegraphics[width=.45\textwidth]{figures/funnel-dup-cropped.pdf} }{%
    \includegraphics[width=.45\textwidth]{figures/funnel-dup-cropped.pdf}} 
  \centering
  \caption{Scyllarus workload reduction%
% Squash citation here; cited in sentence referencing figure.
%~\anoncite{goldman:09Scyllarus}
.}
  \label{fig:workloadReduction}
\end{figure}
